```{r}
library(MASS)
painters
```
# this code will open an file name painters

```{r}
splitted <- split(painters,painters$School)
splitted
```
# this will split the data based on value of the School column in the painters table for eg School name of A are sorted together B are Sorted together and so on

```{r}
tapply(painters$Composition, painters$Expression, mean)
```
# this code is used to find the mean of each column in the painter table which we are using

```{r}
x <- c(1.3, 1.5, 2.5, 3.8, 4.1, 5.9, 7.1, 8.4, 9.0)
xdescrete <- cut(x,breaks = c(-Inf,2,5,8,Inf))  # xdescrete will first create ranges
is.factor(xdescrete)  # display the range in which the given value exist for example 1.3 exit in the range (-Inf,2]
xdescrete
table(xdescrete)   #this will display how many values fall in that interval
```

```{r}
library(readr)
pizza_delivery <- read_csv("~/Documents/Codes/SDA/pizza_delivery.csv")
nrow(na.omit(pizza_delivery))  #this will omit all the values that contains the value na
ecdf_branch <- ecdf(table(pizza_delivery$branch))  # ecdf: Creates the empirical cumulative distribution function (ECDF) for the frequency distribution of the branch column and stores it in the variable ecdf_branch

#Step graph
plot(ecdf_branch,   #plots the values in ecdf_branch
     main = "ECDF of Branches",   #title of the graph
     xlab = "Branch",   #x-axis name
     ylab = "ECDF",   #y-axis name
     col = c('blue', 'green','red'),  #color of the plots
     # if there are less no of colors than points so it rotates and uses these same colors again
     lwd = 2)  #set the line width 2
```
# this code will read the data file and drawing the graph with respect to the points in the table

```{r}
#Step graph for temperature
# You will notice its a line graph but once you zoom in you will see many step graphs
ecdf_temperature <- ecdf((pizza_delivery$temperature)) 
plot(ecdf_temperature,
     main="ECDF of Temperature",
     xlab="temperature",
     ylab="ECDF",
     col = 'blue',
     lwd = 2)
```

```{r}
#bar chart
branchNo = table(pizza_delivery$branch)
barplot(branchNo,
        main="Bar plot for ECDF of Branch",
        xlab="Branch",
        ylab="count",
        col = c('blue','green','red','purple')
       )
```

```{r}
#Pie chart
pie(branchNo,
    main = "Piechart",
    labels = names(table(pizza_delivery$branch)),
    col = c('blue','green','red','purple'))
```
